---
title: "Analysis of coastal heritage survey data from the People of the Guana Peninsula, Florida"
date: now
execute: 
  warning: false
---

```{r}
library(tidyverse)
survey_data <- read_csv("People of the Guana Peninsula Survey_October 3, 2022_12.36.csv")


library(janitor)
# get the first row as the col names
survey_data_q <-
  survey_data %>%
  row_to_names(row_number = 1) %>% 
  slice(-1)

```

## Introduction

Dates that the survey was available... State here how many people filled out the survey

## Demographics

Age Range

```{r}
#| label: fig-age-range
#| fig-cap: "Age Range of Survey Respondents"

survey_data_q_age <- 
survey_data_q  %>%
  select(starts_with("Age Range")) %>%
  pivot_longer(everything()) %>%
  mutate(name = str_remove_all(name, "Age Range")) %>% 
  # should I drop NA's here?
  # drop_na() %>% 
mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("18 - 29",
                              "30 - 39",
                              "40 - 49",
                              "50 - 59",
                              "60 - 69",
                              "70 - 79",
                              "80 or older"))) %>%
   group_by(name, value) %>% 
  summarise(n = n()) 

  # plot
  ggplot(survey_data_q_age) +
    aes(value, n,  fill = value) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name) +
    # make the n value be in integers instead of decimals?
    scale_y_continuous(breaks= scales::pretty_breaks())
```

Ten respondents fall into the 60-69, which is the most populous age range. Around eight respondents did not select their age range/choose to answer. Ages 18-29 and 30-19 have seven respondents each. Five respondents were between 70-79. 50-59 had six respondents while 40-49 had four. Only one respondent selected 80 or older.

As seen in @fig-age-range, ten of the respondents who chose to state their age range are 60-69. Around eight respondents did not select their age range/choose to answer. Ages 18-29 and 30-19 have seven respondents each. Five respondents were between 70-79. 50-59 had six respondents while 40-49 had four. Only one respondent selected 80 or older.

Ethnicity

```{r}
#| label: fig-ethnicity-plot
#| fig-cap: "Ethnicity of Survey Respondents"

survey_data_q_ethnicity <-
  survey_data_q %>% 
  select(starts_with("Ethinicity - Selected Choice")) %>%
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "Ethnicity - Selected Choice")) %>% 
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("Caucasian (non-Hispanic)",
                              "African-American",
                              "Asian/Pacific Islander",
                              "Multi-racial",
                              "Prefer to self-identify as",
                              "Prefer not to answer"))) %>%
  group_by(name, value) %>% 
  summarise(n = n())
  # plot

  ggplot(survey_data_q_ethnicity) +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)

n_caucasian <- survey_data_q_ethnicity %>% 
  filter(value == "Caucasian (non-Hispanic)") %>% 
  pull(n)
```

As seen in @fig-ethnicity-plot, a majority of survey respondents identified as Caucasian and comprised of `r n_caucasian` individuals in the survey. 3 respondents identified as multi-racial, 2 as African American and 1 as Asian/Pacific Islander. 1 respondent chose the 'prefer not to answer' option. (1 person preferred to self-identify as 'human' in the text column). 


As seen in @fig-ethnicity-plot, a majority of survey respondents identified as Caucasian and comprised of `r n_caucasian` individuals in the survey. 3 respondents identified as multi-racial, 2 as African American and 1 as Asian/Pacific Islander. 1 respondent chose the 'prefer not to answer' option. (1 person prefered to self-identify as 'human' in the text column).

Gender Identity

```{r}
#| label: fig-gender-identity
#| fig-cap: "Gender Identities of Survey Respondents"
survey_data_q_gender <- 
survey_data_q %>% 
  select(starts_with("Gender Identity - Selected Choice")) %>%
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "Gender Identity - Selected Choice")) %>% 
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("Female",
                              "Male",
                              "Prefer not to say"))) %>%
  group_by(name, value) %>% 
  summarise(n = n())  

  # plot
  ggplot(survey_data_q_gender) +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)
  
n_female <- survey_data_q_gender %>% 
  filter(value == "Female") %>% 
  pull(n)

n_male <- survey_data_q_gender %>% 
  filter(value == "Male") %>% 
  pull(n)
```

As seen in @fig-gender-identity, most of the survey respondents self-identify as female, at `r n_female`. `r n_male` respondents identify as male, and a few chose not to say. No one wrote in any preferred self-identifier.

highest degree or level of schooling

```{r}
#| label: fig-schooling-plot
#| fig-cap: "Highest Level of Schooling of Survey Respondents"

survey_data_q %>% 
  select(starts_with("Please select the highest degree or level of schooling you have completed")) %>%
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "Please select the highest degree or level of schooling you have completed")) %>% 
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("Master's degree",
                              "Bachelor's degree",
                              "Doctorate degree",
                              "Trade/technical/vocational training",
                              "Some college credit, no degree",
                              "Prefer not to answer"))) %>%
  group_by(name, value) %>% 
  summarise(n = n()) %>% 
  # plot
  ggplot() +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)
  
```

As seen in @fig-schooling-plot, a majority of respondents either hold a bachelor's or master's degree as their highest level of schooling. 16 respondents listed a bachelor's degree as their highest level of school, while 15 individuals hold a master's degree and 4 respondents have a doctorate degree. 3 individuals responded that they have earned some college credits but no degree. 1 respondent has trade/technical,vocational training, and 1 respondent chose the 'prefer not to answer' option.

Zip code

```{r}
library(zipcodeR)
survey_data_q_zip <- 
survey_data_q %>% 
  select(`Zip Code`) %>% 
  drop_na() %>% 
  group_by(`Zip Code`) %>% 
  tally(sort = TRUE) %>% 
  mutate(zp = str_sub(`Zip Code`, 1, 5)) %>% 
  mutate(z_data = map(zp, ~reverse_zipcode(.x))) %>% 
  unnest(z_data) 

zip_2_digits <- 
  as.numeric(unique(str_sub(survey_data_q_zip$zipcode, 1, 2)))

library(sf)
library(tigris)
options(tigris_use_cache = TRUE)

# polygons from zctas
poly_zctas <- 
  zctas(cb = TRUE, 
        starts_with = zip_2_digits) %>%
  left_join(survey_data_q_zip, by = c("ZCTA5CE20" = "zp"))

ggplot() +
  geom_sf(data = poly_zctas, 
          aes(fill = n),
          color = NA) 

```

```{r}
#|label: fig-visit-GTM
#| fig-cap: "Respondents Who Visited GTM Research Reserve"
# Q1: Have you visited the GTM Research Reserve?
survey_data_q  %>%
  select(`Have you visited the GTM Research Reserve?`) %>%
  ggplot() +
    aes(`Have you visited the GTM Research Reserve?`) +
    geom_bar()
```

```{r}
#| label: fig-activities
#| fig-cap: "Activities of Survey Respondents"

# Q2: When you come to the Guana Tolomato Matanzas (GTM) Research Reserve, what kind of activities do you engage in?

survey_data_q_activities <-
survey_data_q  %>%
  select(kind_of_activities = `When you visit the GTM Research Reserve, what kind of activities do you engage in? Check all that apply. - Selected Choice`) %>%
  separate_rows(kind_of_activities, sep = ",") %>% 
  group_by(kind_of_activities) %>% 
  summarise(n = n()) %>% 
  drop_na()

#plot
  ggplot(survey_data_q_activities) +
    aes(reorder(kind_of_activities, 
                n), n) +
    geom_col() +
  coord_flip()

# inline code

n_walking <- survey_data_q_activities %>% 
  filter(kind_of_activities == "Walking") %>% 
  pull(n)

n_hiking <- survey_data_q_activities %>%
  filter(kind_of_activities == "Hiking") %>% 
  pull(n)

n_research <- survey_data_q_activities %>%
  filter(kind_of_activities == "Research") %>% 
  pull(n)

n_volunteering <- survey_data_q_activities %>%
  filter(kind_of_activities == "Volunteering") %>% 
  pull(n)
```

As seen in @fig-activities, the most common activity for that respondents report doing at the GTM Research Reserve is walking, at `r n_walking`. The next most frequent activity is hiking, with `r n_hiking` respondents self-reporting partaking in this activity. More general recreational activities like walking, hiking, and general nature appreciation are more dominant than more specific recreational activities like visiting the beach, photography, bird watching, paddling, exercising, biking, fishing and dog walking. Research is the most dominant non-recreational activity, at `r n_research` survey respondents. Research, General Historic Resources Appreciation, Educational Programming, and Volunteering are non-recreational activities that are clustered together with between `r n_research` and `r n_volunteering` individuals reporting participation in them.

```{r}
#| label: fig-cultural-familiarity
#| fig-cap: "Familiarity With Cultures Through Time"

# Q3: Have you heard of these cultures that used this area through time?
survey_data_q_cultural_familiarity <-
survey_data_q  %>%
  # select the columns relevant to this question
  select(starts_with("Have you heard of these cultures that used this area through time?")) %>%
  pivot_longer(everything()) %>% 
  # remove some of the text that is repetitive here
  mutate(name = str_remove_all(name, "Have you heard of these cultures that used this area through time\\? Please select the option that best describes your relationship with these cultures\\. - ")) %>% 
  # omit NA
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
  mutate(value = fct_relevel(value, 
                             c("I identify as a descendant of this culture.",
                               "I am familiar with this culture.",
                               "I have heard of this culture.",
                               "I have never heard of this culture."))) %>% 

  # tally up
  group_by(name, value) %>% 
  summarise(n = n()) 

  #plot
  ggplot(survey_data_q_cultural_familiarity) +
   aes(value, n) +
   geom_col() +
   coord_flip() +
   facet_wrap( ~name)
  
  
# I want to make sure to refer to cultural groups with the correct language
```

As we can see in @fig-cultural-familiarity, all survey respondents were familiar with the Spanish colonist culture, the Timucua culture, the British colonist culture, and the Seminole culture. More than thirty visitors were familiar with the Spanish colonist culture, as well as with the Timucua culture, and Gullah Geechee culture. Survey respondents were least familiar with the Guale culture, and the ancestral period native cultures.

```{r}
#|label:fig-cultural-resources-familiarity
#| fig-cap: "Familiarity With Cultural Resources"

# Q4: How familiar are you with these types of cultural resources?

survey_data_q  %>%
  # select the columns relevant to this question
  select(starts_with("How familiar are you with these types of cultural resources?")) %>%
  pivot_longer(everything()) %>% 
  # remove some of the text that is repetitive here
  mutate(name = str_remove_all(name, "How familiar are you with these types of cultural resources\\? - ")) %>% 
  # omit NA
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Extremely familiar",
                              "Very familiar",
                              "Slightly familiar",
                              "Moderately familiar",
                              "Not familiar at all"))) %>%
  # tally up
  group_by(name, value) %>% 
  summarise(n = n()) %>% 
  # plot
  ggplot() +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)

#Would simplifying familiarity be useful here?
```

In @fig-cultural-resources, we can see that all survey respondents are at least moderately familiar with the shipwrecks and historic cemeteries, as none report being "not familiar at all" with these cultural resources. Around fourteen people report being very familiar with the wells. More than fiften people are only slightly familiar with the canals in the area. Respondents are most unfamiliar with the remains of industrial activity, shell rings, as well as ship hards, docks, and wharves. Less than five respondents report being unfamiliar with mounds, canals, "slave" cabins, Spanish missions, remains of agricultural activity, shell middens, and plantations.

```{r}
#|label: fig-encountering-resources
#| fig-cap: "Encountering Cultural Resources at the GTM Research Reserve"

# Q5: Have you encountered any of these cultural resources while at the GTM Research Reserve? 

survey_data_q %>% 
  select(starts_with("Have you encountered any of these cultural resources while at the GTM Research Reserve?")) %>%
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "Have you encountered any of these cultural resources while at the GTM Research Reserve\\? - ")) %>% 
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("Never Encountered",
                              "Rarely Encountered",
                              "Frequently Encountered",
                              "Unsure"))) %>%
  group_by(name, value) %>% 
  summarise(n = n()) %>% 
  # plot
  ggplot() +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)
#should facet be reordered so that it is consistent between the q4 plot of unfamiliar-> familiar, and never encountered-> frequently encountered?
```

@fig-encountering-resources shows that more than twenty survey respondents have never encountered "slave" cabins, the remains of industrial activity or Spanish missions respectively, at the GTM Research Reserve. Almost twenty respondents report that they have never encountered plantations, ship hards, docks, and wharves, or shipwrecks each, at the reserve. Shell Middens are the most frequently encountered cultural resource at the GTM Research Reserve, with more than fifteen respondents. Respondents are most unsure as to whether or not they have encountered shell rings at the GTM Research reserve. We can also see that respondents  report encountering wells with some level of frequency, more encountering them overall than not.

```{r}
#|label: fig-effects-climate-change
#| fig-cap: "Noticing the Effects of Climate Change"

# Q7. Have you noticed or experienced any of the following effects from climate change while visiting the Reserve?
# There is definitely a better and more legible way to do this. I want to reorder the axes and see if that helps, but I'm sure there's a faster way to pull.

survey_data_q  %>%
  select(starts_with("Have you noticed or experienced any of the following effects from climate change while visiting the Reserve?")) %>% 
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "Have you noticed or experienced any of the following effects from climate change while visiting the Reserve\\? - ")) %>% 
  drop_na() %>% 
mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("Increased Coastal Erosion",
                              "Increased Flooding Events",
                              "Increased Frequency and/or Severity of Storm Surge",
                              "Higher Water Table",
                              "Increased and Intensified Storm Events",
                              "Increased Temperatures",
                              
                              "Changes in Seasonality",
                              "Species Shifts/Extinctions"))) %>%
  group_by(name, value) %>% 
  summarise(n = n()) %>%
  #plot
  ggplot() +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)
```

Respondents overwhelmingly report that they have noticed increased coastal erosion at the GTM research reserve, at more than 25, as seen in @fig-effects-climate-change. Changes in seasonality, a high water table, and species shifts or extinctions are less prominently noticed at the reserve. Other more noticeable effects of climate change are increased and intensified storm events, increased flooding events, increasing temperatures, and increasing frequency or severity of storms, with more than fifteen respondents reporting that they notice or have experienced these effects a lot at the reserve.

```{r}
#|label: fig-threat-cultural
#| fig-cap: "Percieved Threats to Cultural Resources"

# Q8. What do you see as the biggest threat to cultural resources? 

survey_data_q  %>%
  select(starts_with("What do you see as the biggest threat to cultural resources?")) %>% 
  select(- ends_with("Text")) %>% 
  pivot_longer(everything()) %>% 
  mutate(name = str_remove_all(name, "What do you see as the biggest threat to cultural resources\\? Please drag the choices to rank them with the most threatening as 1\\. - ")) %>% 
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
  group_by(name, value) %>% 
  summarise(n = n()) %>% 
  ggplot() +
    aes(value, n) +
    geom_col() +
    coord_flip() +
    facet_wrap( ~ name)

#Omitted the column containing free text (other). Is there a better way to do Q8?

# would color be a good addition for visualizing the gradation of threat?

```
In @fig-threat-cultural, we can see that respondents percieve sea level rise as a major threat to the cultural resources at the reserve, more than ten respondents ranking it as the top threat to cultural resources. Increasing and intensified storm events are clustered around higher degrees of the threat to cultural resources, at six or higher. Notably, almost fifteen respondents rank flooding as the third most threatening effect of climate change to the reserve. Development is also ranked as the top threat to resources by more than ten survey respondents. Overuse, infrastructure, and management issues are perceived as less threatening by survey respondents. Noticeably, aside from development, climate change related threats, including sea level rise, increased and intensified storm events, and flooding, are ranked by most survey respondents as the greatest threats to the reserve. 

How about age and activity?

```{r}
#|label: fig-age-activity
#| fig-cap: "Activity by Age"

survey_data_q_activity_age <- 
survey_data_q %>% 
  select(starts_with("Age Range"),
         kind_of_activities = `When you visit the GTM Research Reserve, what kind of activities do you engage in? Check all that apply. - Selected Choice`) %>% 
  separate_rows(kind_of_activities, sep = ",") %>% 
  group_by(`Age Range`, kind_of_activities  ) %>% 
  tally() 

  ggplot(survey_data_q_activity_age) +
  aes(x = kind_of_activities,
      y = n,
      fill = `Age Range`) +
   geom_bar(position="fill", stat="identity") +
  theme(axis.text.x  = element_text(size = 3)) +
coord_flip()
```

In @fig-age-activity, we can observe that all survey respondents who walk their dogs while visiting the reserve fall within the age range of 40-49. As we saw in @fig-activities, the most common activities among survey respondents included walking, hiking, and general nature appreciation, with more than twenty respondents reporting partaking in each of these activities. In @fig-age-activity, we can see overlap. The most common activities involving respondents distributed across each of seven out of the eight age ranges, are walking, general nature appreciation, and general historic resources appreciation. Research is also among these in @fig-age-activity, with seven out of the eight age ranges partaking in this activity while at GTM. The activity undertaken in the greatest proportion for the 18-29 age range is general resources appreciation, comprising one quarter of those who participate in that activity. Notably, at the most numerous age range, including ten respondents, indivudals ranging between 60-69 comprise varying proportion of every activity, except dog walking. 
Age by awareness of cultural resources

```{r}
#|label: fig-age-awareness-cultural-res
#| fig-cap: "Awareness of Cultural Resources by Age"
survey_data_q %>% 
  select(starts_with("Age Range"),
         starts_with("How familiar are you with these types of cultural resources?")) %>% 
 pivot_longer(-`Age Range`) %>% 
  # remove some of the text that is reptitive here
  mutate(name = str_remove_all(name, "How familiar are you with these types of cultural resources\\? - ")) %>% 
  # omit NA
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Extremely familiar",
                              "Very familiar",
                              "Slightly familiar",
                              "Moderately familiar",
                              "Not familiar at all"))) %>%
  mutate(simple_familarity = ifelse(value %in% c("Extremely familiar", "Very familiar"), "familiar", "unfamiliar")) %>% 
  # tally up
  group_by(`Age Range`, name, simple_familarity) %>% 
  summarise(n = n()) %>% 
  filter(simple_familarity == "familiar") %>% 
  ggplot() +
  aes(`Age Range`,
      n, fill = `Age Range`) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-age-awareness-cultural-res...
Age by cultures encountered

```{r}
#|label: fig-age-encountering-cultural-res
#| fig-cap: "Encountering Cultural Resources by Age"
survey_data_q %>% 
  select(starts_with("Age Range"),
         starts_with("Have you encountered any of these cultural resources while at the GTM Research Reserve?")) %>% 
 pivot_longer(-`Age Range`) %>% 
  mutate(name = str_remove_all(name, "Have you encountered any of these cultural resources while at the GTM Research Reserve\\? - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Frequently Encountered",
                              "Rarely Encountered",
                              "Never Encountered",
                              "Unsure"))) %>%
  mutate(simple_encounter = ifelse(value %in% c("Frequently Encountered", "Rarely Encountered"), "encountered", "not encountered")) %>% 
  group_by(`Age Range`, name, simple_encounter) %>% 
  summarise(n = n()) %>% 
  filter(simple_encounter == "encountered") %>% 
  ggplot() +
  aes(`Age Range`,
      n) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
  
```
In @fig-age-encountering-cultural-res
Activity and Level of Education

```{r}
#|label: fig-activity-schooling
#| fig-cap: "Activities at the GTM by Level of Schooling"

survey_data_q %>% 
  select(schooling = starts_with("Please select the highest degree or level of schooling you have completed"),
         kind_of_activities = `When you visit the GTM Research Reserve, what kind of activities do you engage in? Check all that apply. - Selected Choice`) %>% 
  separate_rows(kind_of_activities, sep = ",") %>%
  drop_na() %>% 
  mutate(value = str_squish(schooling)) %>% 
  mutate(value = fct_relevel(schooling,
                            c("Master’s degree",
                              "Bachelor’s degree",
                              "Doctorate degree",
                              "Trade/technical/vocational training",
                              "Some college credit, no degree",
                              "Prefer not to answer"))) %>%
  mutate(schooling = case_when(
    schooling == "Master’s degree" ~ "has a degree",
    schooling == "Bachelor’s degree" ~ "has a degree",
    schooling == "Doctorate degree" ~ "has a degree",
    schooling == "Trade/technical/vocational training" ~ "no degree",
    schooling == "Some college credit, no degree" ~ "no degree",
    TRUE ~ "other"
  )) %>% 
  group_by(kind_of_activities, schooling) %>% 
  summarise(n = n()) %>% 
  ggplot() +
  aes(schooling, n) +
  geom_col() +
  facet_wrap( ~ kind_of_activities, scales = "free_y") +
  theme(axis.text.x  = element_text(size = 3))

```
In @fig-activity-schooling...

Awareness of cultural resources by Level of Education

```{r}
#|label: fig-edu-awareness-cult-res
#| fig-cap: "Awareness of Cultural Resources by Level of Education"
survey_data_q %>% 
  select(schooling = starts_with("Please select the highest degree or level of schooling you have completed"),
         starts_with("How familiar are you with these types of cultural resources?"))  %>% 
     pivot_longer(-schooling) %>% 
   mutate(name = str_remove_all(name, "How familiar are you with these types of cultural resources\\? - ")) %>% 
   drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Extremely familiar",
                              "Very familiar",
                              "Slightly familiar",
                              "Moderately familiar",
                              "Not familiar at all"))) %>%
  mutate(simple_familarity = ifelse(value %in% c("Extremely familiar", "Very familiar"), "familiar", "unfamiliar")) %>% 
    mutate(schooling = case_when(
    schooling == "Master’s degree" ~ "has a degree",
    schooling == "Bachelor’s degree" ~ "has a degree",
    schooling == "Doctorate degree" ~ "has a degree",
    schooling == "Trade/technical/vocational training" ~ "no degree",
    schooling == "Some college credit, no degree" ~ "no degree",
    TRUE ~ "other"
  )) %>% 
  # tally up
  group_by(schooling, name, simple_familarity) %>% 
  summarise(n = n()) %>% 
  filter(simple_familarity == "familiar") %>% 
  ggplot() +
  aes(schooling,
      n) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 5))

```
In @fig-edu-awareness-cult-res
Awareness of cultural resources by ethnicity

```{r}
#|label: fig-ethnicity-awareness-cult-res
#| fig-cap: "Awareness of Cultural Resources by Ethnicity"
survey_data_q %>% 
  select(Ethnicity = starts_with("Ethinicity - Selected Choice"),
         starts_with("How familiar are you with these types of cultural resources?")) %>% 
 pivot_longer(-`Ethnicity`) %>% 
  mutate(name = str_remove_all(name, "How familiar are you with these types of cultural resources\\? - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Extremely familiar",
                              "Very familiar",
                              "Moderately familiar",
                              "Slightly familiar",
                              "Not familiar at all"))) %>%
  mutate(simple_familiarity = ifelse(value %in% c("Extremely familiar", "Very familiar"), "familiar", "not familiar")) %>% 
  group_by(`Ethnicity`, name, simple_familiarity) %>% 
  summarise(n = n()) %>% 
  filter(simple_familiarity == "familiar") %>% 
  ggplot() +
  aes(`Ethnicity`,
      n) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-ethnicity-awareness-cult-res, since most of the survey respondents identify as Caucasian... different vis?
Awareness of cultural resources by gender

```{r}
#|label: fig-gender-awareness-cult-res
#| fig-cap: "Awareness of Cultural Resources by Gender"
survey_data_q_awareness_gender <- 
survey_data_q %>% 
  select(Gender = starts_with("Gender Identity - Selected Choice"),
         starts_with("How familiar are you with these types of cultural resources?")) %>% 
 pivot_longer(-`Gender`) %>% 
  mutate(name = str_remove_all(name, "How familiar are you with these types of cultural resources\\? - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Extremely familiar",
                              "Very familiar",
                              "Moderately familiar",
                              "Slightly familiar",
                              "Not familiar at all"))) %>%
  mutate(simple_familiarity = ifelse(value %in% c("Extremely familiar", "Very familiar"), "familiar", "not familiar")) %>% 
  group_by(`Gender`, name, simple_familiarity) %>% 
  summarise(n = n()) %>% 
  filter(simple_familiarity == "familiar") 

  ggplot(survey_data_q_awareness_gender) +
  aes(`Gender`,
      n) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
  
    ggplot(survey_data_q_awareness_gender) +
  aes(x = name,
      y = n,
      fill = Gender) +
   geom_bar(position="fill", stat="identity") +
  theme(axis.text.x  = element_text(size = 3)) +
coord_flip()
```
In @fig-gender-awareness-cult-res
Cultures encountered by ethnicity

```{r}
#|label: fig-ethnicity-encountered-cult-res
#| fig-cap: "Encountered Cultural Resources by Ethnicity"
survey_data_q_culture_by_ethnicity <- 
survey_data_q %>% 
  select(Ethnicity = starts_with("Ethinicity - Selected Choice"),
         starts_with("Have you encountered any of these cultural resources while at the GTM Research Reserve?")) %>% 
 pivot_longer(-`Ethnicity`) %>% 
  mutate(name = str_remove_all(name, "Have you encountered any of these cultural resources while at the GTM Research Reserve\\? - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Frequently Encountered",
                              "Rarely Encountered",
                              "Never Encountered",
                              "Unsure"))) %>%
  mutate(simple_encounter = ifelse(value %in% c("Frequently Encountered", "Rarely Encountered"), "encountered", "not encountered")) %>% 
  group_by(`Ethnicity`, name, simple_encounter) %>% 
  summarise(n = n()) %>% 
  filter(simple_encounter == "encountered")  %>% 
  filter(!Ethnicity  %in% c("Prefer to self-identify as:",
                             "Prefer not to answer"))

ggplot(survey_data_q_culture_by_ethnicity) +
  aes(x = name,
      y = n,
      fill = Ethnicity) +
   geom_bar(position="fill", stat="identity") +
  theme(axis.text.x  = element_text(size = 3)) +
coord_flip()
```
In @fig-ethnicity-encountered-cult-res
Cultures encountered by Gender

```{r}
#|label: fig-gender-encountered-cult-res
#| fig-cap: "Encountered of Cultural Resources by Gender"
survey_data_q %>% 
  select(Gender = starts_with("Gender Identity - Selected Choice"),
         starts_with("Have you encountered any of these cultural resources while at the GTM Research Reserve?")) %>% 
 pivot_longer(-`Gender`) %>% 
  mutate(name = str_remove_all(name, "Have you encountered any of these cultural resources while at the GTM Research Reserve\\? - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("Frequently Encountered",
                              "Rarely Encountered",
                              "Never Encountered",
                              "Unsure"))) %>%
  mutate(simple_encounter = ifelse(value %in% c("Frequently Encountered", "Rarely Encountered"), "encountered", "not encountered")) %>% 
  group_by(`Gender`, name, simple_encounter) %>% 
  summarise(n = n()) %>% 
  filter(simple_encounter == "encountered") %>% 
  ggplot() +
  aes(`Gender`,
      n) +
  geom_col(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-gender-encountered-cult-res
Biggest threat by age

```{r}
#|label: fig-age-threat
#| fig-cap: "Perceived Threat to Cultural Resources by Age"
survey_data_q %>% 
  select(starts_with("Age Range"),
         starts_with("What do you see as the biggest threat to cultural resources?"),
         -ends_with("Text")) %>% 
 pivot_longer(-`Age Range`) %>% 
  mutate(name = str_remove_all(name, "What do you see as the biggest threat to cultural resources\\? Please drag the choices to rank them with the most threatening as 1\\. - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("9",
                              "8",
                              "7",
                              "6",
                              "5",
                              "4",
                              "3",
                              "2",
                              "1"))) %>%
  group_by(`Age Range`, name, value) %>% 
  summarise(n = n()) %>% 
  ggplot() +
  aes(`Age Range`,
      value) +
  geom_point(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-age-threat
Biggest Threat by ethnicity

```{r}
#|label: fig-ethnicity-threat
#| fig-cap: "Perceived Threat to Cultural Resoures by Ethnicity "
survey_data_q %>% 
  select(Ethnicity = starts_with("Ethinicity - Selected Choice"),
         starts_with("What do you see as the biggest threat to cultural resources?"),
         -ends_with("Text")) %>% 
 pivot_longer(-`Ethnicity`) %>% 
  mutate(name = str_remove_all(name, "What do you see as the biggest threat to cultural resources\\? Please drag the choices to rank them with the most threatening as 1\\. - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("9",
                              "8",
                              "7",
                              "6",
                              "5",
                              "4",
                              "3",
                              "2",
                              "1"))) %>%
  group_by(`Ethnicity`, name, value) %>% 
  summarise(n = n()) %>% 
  ggplot() +
  aes(`Ethnicity`,
      value) +
  geom_point(position="dodge") +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-ethnicity-threat...
Biggest Threat by Gender

```{r}
#|label: fig-gender-threat
#| fig-cap: "Perceived Threat to Cultural Resources by Gender"
survey_data_q %>% 
  select(Gender = starts_with("Gender Identity - Selected Choice"),
         starts_with("What do you see as the biggest threat to cultural resources?"),
         -ends_with("Text")) %>% 
 pivot_longer(-`Gender`) %>% 
  mutate(name = str_remove_all(name, "What do you see as the biggest threat to cultural resources\\? Please drag the choices to rank them with the most threatening as 1\\. - ")) %>% 
  drop_na() %>% 
  # omit spaces at the start and end of the text
  mutate(value = str_squish(value)) %>% 
  # order a factor so that the plot has logically ordered bars
 mutate(value = fct_relevel(value,
                            c("9",
                              "8",
                              "7",
                              "6",
                              "5",
                              "4",
                              "3",
                              "2",
                              "1"))) %>%
  group_by(`Gender`, name, value) %>% 
  summarise(n = n()) %>% 
  ggplot() +
  aes(`Gender`,
      value) +
  geom_point() +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-gender-threat
Biggest Threat by level of education

```{r}
#|label: fig-edu-threat
#| fig-cap: "Percieved Threat to Cultural Resources by Level of Education"
survey_data_q %>% 
  select(schooling = starts_with("Please select the highest degree or level of schooling you have completed"),
         starts_with("What do you see as the biggest threat to cultural resources?"),
         -ends_with("Text")) %>% 
  pivot_longer(-`schooling`) %>% 
  mutate(name = str_remove_all(name, "What do you see as the biggest threat to cultural resources\\? Please drag the choices to rank them with the most threatening as 1\\. - ")) %>%
  mutate(schooling = case_when(
    schooling == "Master’s degree" ~ "has a degree",
    schooling == "Bachelor’s degree" ~ "has a degree",
    schooling == "Doctorate degree" ~ "has a degree",
    schooling == "Trade/technical/vocational training" ~ "no degree",
    schooling == "Some college credit, no degree" ~ "no degree",
    TRUE ~ "other"
  )) %>%
  drop_na() %>% 
  mutate(value = str_squish(value)) %>% 
 mutate(value = fct_relevel(value,
                            c("9",
                              "8",
                              "7",
                              "6",
                              "5",
                              "4",
                              "3",
                              "2",
                              "1"))) %>%
  group_by(`schooling`, name, value) %>% 
  summarise(n = n()) %>% 
  ggplot() +
  aes(`schooling`,
      value) +
  geom_point() +
  facet_wrap( ~ name) +
  theme(axis.text.x  = element_text(size = 3))
```
In @fig-edu-threat...